SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-08 scipy-1.0/paper.tex
Added citation for continuous integration from @tylerjereddy

\subsection*{SciPy Today}
At the time of writing, the SciPy library consists of nearly
\num{600000}~lines of code organized in 16~subpackages. The development
team and community currently interact and operate primarily
on GitHub, an online version control and task management platform.
Over \num{110000}~GitHub repositories and \num{6500}~packages depend
on SciPy\cite{dependents}. Some of the major
feature highlights from the three years preceding
SciPy 1.0 are discussed in the Key Technical Improvements section below,
and milestones in its history are highlighted in Figure~\ref{fig:timeline}.
% At the time of writing, SciPy produces a new release
% approximately every six months, and some of the major
% feature highlights from the three years preceding
% SciPy 1.0 are discussed in a technical improvements
% section below. Some longer-term milestone events are
% highlighted in Figure~\ref{fig:timeline}.

@@

Test-driven development has been described as a way to manage fear and
uncertainity when making code changes\cite{TDD-Beck}. For each component of SciPy, we write multiple small executable
tests that verify its intended behavior. The collection of these, known as a \emph{test suite}, increases confidence in
the correctness and accuracy of the library, and lets us make code modifications known not to alter desired behavior. Monitoring the number of lines
of code in SciPy covered by unit tests is one way we maintain
some certainty that changes and new features are correctly implemented.
The SciPy test suite is orchestrated by a continuous integration matrix that
includes POSIX and Windows (32/64-bit) platforms managed by Travis CI and
AppVeyor, respectively. Our tests cover Python versions 2.7, 3.4, 3.5, 3.6, and
include code linting with \texttt{pyflakes} and \texttt{pycodestyle}. There
are more than \num{13000}~unit tests in the test suite, which is written for usage
with the \texttt{pytest}\cite{pytest} framework.
Test coverage at the SciPy~1.0 release point (Figure~\ref{fig:coverage}) was at
87\% for Python code according to \texttt{pytest-cov}\cite{pytest-cov} and
45\% for compiled (C, C++, and Fortran) code according to \texttt{gcov}\cite{gcov}.
Documentation for the code is automatically built and published by
the CircleCI service to facilitate evaluation of documentation changes /
integrity.  Our full test suite also passes with PyPy3\cite{Bolz:2009:TMP:1565824.1565827}, a just-in-time compiled
version of the Python language.

>>>>

\subsection*{SciPy Today}
At the time of writing, the SciPy library consists of nearly
\num{600000}~lines of code organized in 16~subpackages.
Over \num{110000}~GitHub repositories and \num{6500}~packages depend
on SciPy\cite{dependents}. Some of the major
feature highlights from the three years preceding
SciPy 1.0 are discussed in the Key Technical Improvements section below,
and milestones in its history are highlighted in Figure~\ref{fig:timeline}.
% At the time of writing, SciPy produces a new release
% approximately every six months, and some of the major
% feature highlights from the three years preceding
% SciPy 1.0 are discussed in a technical improvements
% section below. Some longer-term milestone events are
% highlighted in Figure~\ref{fig:timeline}.

@@

Test-driven development has been described as a way to manage fear and
uncertainity when making code changes\cite{TDD-Beck}. For each component of 
SciPy, we write multiple small executable tests that verify its intended
behavior. The collection of these, known as a \emph{test suite}, increases
confidence in the correctness and accuracy of the library, and lets us make
code modifications known not to alter desired behavior.
According to the practice of continuous integration\cite{silver2017collaborative}, all proposed contributions
to SciPy are temporarily integrated with the master branch of the library
before the test suite is run, and all tests must pass before the contribution
is permanently merged.
Continuously monitoring the number
of lines of code in SciPy covered by unit tests is one way we maintain
some certainty that changes and new features are correctly implemented.

The SciPy test suite is orchestrated by a continuous integration matrix that
includes POSIX and Windows (32/64-bit) platforms managed by Travis CI and
AppVeyor, respectively. Our tests cover Python versions 2.7, 3.4, 3.5, 3.6, and
include code linting with \texttt{pyflakes} and \texttt{pycodestyle}. There
are more than \num{13000}~unit tests in the test suite, which is written for usage
with the \texttt{pytest}\cite{pytest} framework.
Test coverage at the SciPy~1.0 release point (Figure~\ref{fig:coverage}) was at
87\% for Python code according to \texttt{pytest-cov}\cite{pytest-cov} and
45\% for compiled (C, C++, and Fortran) code according to \texttt{gcov}\cite{gcov}.
Documentation for the code is automatically built and published by
the CircleCI service to facilitate evaluation of documentation changes /
integrity.  Our full test suite also passes with PyPy3\cite{Bolz:2009:TMP:1565824.1565827}, a just-in-time compiled
version of the Python language.
